\dispRity quick demo

### 2015-11-18 doc/dispRity-quick-demo.Rnw
Rewriting vignettes INIT

\title{dispRity demo}

\author{Thomas Guillerme}

@@

This is a quick demo to go through the beta version of the \dispRity package (v.\Sexpr{packageVersion("dispRity")}).
Many parts are still missing (see section \ref{whatsleft}) but this version should be running all right and give an idea of what's implemented in the package.

\section{Before starting}

>>>>

\title{\dispRity quick demo}

\author{Thomas Guillerme\\guillert@tcd.ie}

@@

This is quick demo aiming to give a quick overview of the \dispRity package (v.\Sexpr{packageVersion("dispRity")}).
Please refer to \href{https://github.com/TGuillerme/dispRity}{GitHub page: github.com/TGuillerme/dispRity} for other vignettes, namely the \dispRity tutorial that explains the functions in more details.

To keep it short, this package allows to summarise ordinated matrices (e.g. MDS, PCA, PCO, PCoA) into values called \textbf{disparity}. It then allows to visualise and analyse the disparity of the ordinated matrices.

This demo, which will use dummy data will quickly cover the following points:
\begin{enumerate}
\item 
\end{enumerate}

\section{Installation}
You can install this package easily if you are using the latest version of \R and \texttt{devtools}.

\section{}
